---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# deltasurvey

<!-- badges: start -->
<!-- badges: end -->

The intent of this package is to aid data scientists in analyzing the California Delta Residents Survey of 2023. 

## Installation

At the time of this writing, there is no CRAN version, so must install the development version of deltasurvey from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ktomari/deltasurvey")
```

## Example

First, we'll need a sample from the data set.

```{r data_sample}
data <- data.frame(
  DRS_ID = paste0("DRS", 2:6),
  Q2 = c("<I don't know>", rep("Historic or Delta \"legacy\" town", 4))
)
```

While this function is rarely called on its own, we'll start by looking at a component of the function that reads the data into the R environment. This component allows the reading function to convert angle bracketed values (eg. `"<Missing>"`) to `NA`.

```{r basics1}
library(tidyverse)
library(deltasurvey)

drs_as_NA(data)
```
